Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-08-13 doc/main_jfm.tex
updates
yny

\section{\label{intro}Introduction}

\section{Governing  Equations}
\subsection{\label{mobility}Mobility Problem}
We consider a suspension of $N_b$ particles suspended in a
two-dimensional unbounded domain. The boundary of each particle is
denoted by $\Gamma_i$ so that $\bd \Omega = \Gamma_1 \cup \Gamma_2 \cup
\cdots \cup \Gamma_{N_b}$. Assuming the flow is Stokesian, the governing
equations are
\begin{alignat}{3}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
    && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
%
where $\uu$ is the velocity, $\mu$ is viscosity, $p$ is the pressure,
and $\uu_\infty$ is the background flow. Since each particle $\Gamma_i$
with center $\aa_i$ is a rigid body, its velocity satisfies 
\begin{align}
  \vv(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
    \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is its translational velocity and $\omega_i$ is its
angular velocity. Here, $\langle x, y \rangle^{\perp} = \langle -y, x
\rangle$. Therefore, the no-slip boundary condition on each particle is
\begin{align}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
    \xx \in \Gamma_i.
\end{align}
To determine the translational and angular velocities of each particle,
we assume some imposed forces $\FF_i$ and torques $T_i$ acting on each
particle. Since the small particles are intertialess, force balance
gives 
\begin{alignat}{2}
  \label{eqn:force}
  \FF_i &+ \int_{\Gamma_i} \ssigma \cdot \nnu_i \, ds = \mathbf{0},
  && i=1,\ldots,N_b,\\
  \label{eqn:torque}
  T_i &+ \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
    (\ssigma \cdot \nnu_i) \, ds = 0, \qquad && i=1,\ldots,N_b,
\end{alignat}
where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
\right)$ is the hydrodynamic stress tensor (pressure tensor). The
process of finding the translational and angular velocities given a
force and torque is referred to as the mobility problem.

@@

In order to examine the dynamics of the Janus-vesicle using the HAP coupling with hydrodynamics interactions, for the target bilayer, a circular initial shape is chosen to perform the relaxation run. 
This vesicle-like structure consists of $N=58$ disks with particle radius $r=0.5$ and the starting diameter of 
the vesicle is about $8$ length units.
The starting center of mass position of the Janus-vesicle is pinned at the origin and particle velocities are tracked to determine the initial configuration for later use such as single and multiple vesicle simulations. 
This will prevent some numerical instability issues when the minimum of the total energy is not achieved. 
For instance, the dynamics of the bilayer under a shear flow may reach different outcomes.
Figure~\ref{figure2}(a) shows that the magnitudes of mean velocity components ${\bf v}=\{v_x,v_y\}$ decrease exponentially with an approximation decaying rate $\sim0.005$. In the same figure, the variation of the mean particle orientation $\theta$ also decreases over a period of time as expected from the self-assembly property of the model. This implies that a local energy minimum and the equilibrium configuration are 
nearly attained. 
The time step size $\Delta t=0.2$ is used for all simulations in this work including the relaxation run.
Figure~\ref{figure2}(b) shows the configuration difference between starting and ending frames in the relaxation run. The Figure~\ref{figure2}(c)-(d) demonstrate the fluid pressure profile of two configurations. The pressure inside the permeable Janus-vesicle decreases as expected.

@@

Following the relaxation experiments of the Janus-vesicle, this section will focus on the behavior of vesicles 
under a number of flow types. To extract physical quantities of the target structure using the proposed model, the scaling laws and the dimensionless units are given as follows.
The length unit is scaled by the length of phospholipids $l=2.5$ nm and the force is scaled from the 
interfacial tension $\gamma=4.11$ pN nm$^{-1}$ from ~\cite{Ryham16}. We then be able to calculate the characteristic time scale $\tau = \mu l/\gamma = 0.61$ ns where the fluid viscosity $\mu=1$ cP. With the same framework, \cite{Fu20} provides the bending rigidity $\kappa=8.51$ $k_BT$.
%
The dimensionless shear rate is given by $\chi = \dot\gamma \tau$ where $\dot\gamma$ 
is the shear rate.

%For the $N$-body Janus-vesicle, we denote a constant initial radius $R_0=\sqrt{A_0/4\pi}$ with initial area $A_0$

%referred from~\cite{Finken08} and~\cite{Shaqfeh11},
%\begin{align}
%  \chi = \dot\gamma \frac{\mu R_0^3}{\kappa},
%\end{align}
%%
%where $\dot\gamma$ the dimensional shear rate, and $\mu$ the fluid viscosity.

@@

\begin{table}
\caption{Friction Coefficients}
\centering    
\begin{tabular}{c c c c c c c c }
\hline                    
$\dot\gamma$ (ns$^{-1}$) & 0.0033 & 0.0041 & 0.0049 & 0.0057 & 0.0066 & 0.0074 & 0.0082\\
\hline 
$F_{f}$ (pN nm$^{-1}$)           &  &  &  &  &  &  &   \\[1ex]
$\dot\theta$ (ns$^{-1}$)           &  &  &  &  &  &  & \\ [1ex]
$b$ (pN$\cdot$ns nm$^{-2}$)   &  &  &  &  &  &  & \\ 
\hline    
\end{tabular} 
\label{table1}
\end{table}

@@

\begin{figure}
\centering
\includegraphics[height=2in]{N116_ext_0.pdf}
\includegraphics[height=2in]{N116_ext_2000.pdf}\\
\includegraphics[height=2in]{N116_ext_4000.pdf}
\includegraphics[height=2in]{N116_ext_6500.pdf}
  \caption{Two vesicles under an extensional flow where the dimensioneless shear rate is $\dot\gamma=0.005$; The initial configuration is shown in panel (a). The background color indicates the magnitude of fluid pressure. From dark red to dark blue, it represents the the pressure varies from high to low values. The color bar is valid for all panels. Streamlines are plotted in purple. The insets show the results produced from using continuum model that the streamlines have perfect agreements with the present results.
  }
    \label{figure9}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.9\textwidth]{ExtTraj.eps}
\end{center} 
  \caption{Trajectories of different setups in two-vesicle in an extensional flow where the centroids of two Janus-vesicle are plotted as blue dots. (i) Both centroids of two Janus-vesicles are on the $x$-axis; (ii) The centroid of the left Janus-vesicle is $0.1$ unit above the $x$-axis; (iii) 
  The centroid of the left Janus-vesicle is $0.1$ unit above the $x$-axis and the other one is $0.1$ unit below the $x$-axis; (iv) The centroid of the left Janus-vesicle is $0.5$ unit above the $x$-axis and the other one is $0.5$ unit below the $x$-axis; Figure~\ref{figure9} presents the numerical results from the case (iii) and a 
  consistent flow rate is $\chi = 0.005$ for all cases.}
    \label{figure10}
\end{figure}

>>>>

\section{\label{intro}Introduction}
Described by de Gennes as ``another animal in soft matter physics", the Janus particle (often a spherical particle with a hydrophobic and a hydrophilic hemisphere) exhibits complex aggregate, clustering and self-assembly into meso- and macroscopic structures that are relevant to a wide range of applications in biology and bioengineering. Whether it is surface chemistry or polarity under an external field, the dynamics of Janus particles is inevitably the combination of long-range hydrodynamics interactions in the presence of short- and intermediate-range particle-particle interactions.

Recently Fu {\it et al.} illustrated that the hydrophobic interactions between Janus particles in a viscous solvent can be used as a coarse-grained model to capture the mechanics of an elastic bilayer membrane of amphiphilic macromolecules such as lipids \cite{Fu2020_SIAM}. Depending on the total number of Janus particles and their geometry, in a viscous solvent, Janus particles are found to aggregate to form a micelle, a patch of bilayer membrane with open ends, and a self-enclosed bilayer membrane (a vesicle). Using a hybrid continuum model for the interactions between amphiphilic particles in a viscous solvent and formulating it in a boundary integral formulation, Fu {\it et al.} showed that the membrane granularity during fusion and fission of bilayers can be accurately captured. 
%This boundary integral formulation has inspired more recent work

In molecular dynamics (MD) simulations, the lipid bilayer membranes are often approximated by an implicit solvent coarse-grained model for lipids (as in the Martini code), where their hydrodynamic interactions are simplified by an implicit solvent. The long-range hydrodynamic interactions and the induced long-range lipid interactions can be captured by combining the Dry Martini with a lattice Boltzmann MD \cite{Brandner2019_SciRep}. Brandner {\it et al.} used this methodology to simulate the hydrodynamics of a nano-sized vesicle under a shear flow, and reproduced the well-know vesicle hydrodynamics  such as tank-treading, tumbling and inter-leaflet slippage (reported from simulations of the Helfrich-type continuum model).

In this work we extend the hybrid continuum model in \cite{Fu2020_SIAM} for the Janus suspension to incorporate the collective hydrodynamics of a Janus suspension under various flows: a linear shear flow, an elongation flow, and a Poiseuille flow. We demonstrate that a vesicle made of Janus particles does behave like a vesicle in these flowing conditions. Furthermore we also show that the hybrid continuum model allows us to investigate the inter-leaflet slippage and rupture of a bilayer membrane due to an imposed flow.

This paper is organized as follows. In \S~\ref{sec:governing_eqs} we present the formulation for the Janus particles in a viscous fluid in the zero-Reynolds number regime. In \S~\ref{sec:IEM} we extend the hybrid continuum model for a Janus suspension to include the effects of a far-field flow via the mobility problem formulation. In \S~\ref{validation} we present validation of our model, and in \S~\ref{results} we present simulation results for a vesicle of Janus bilayer membrane under various flowing conditions. Finally we provide discussion and outlook for future directions in \S~\ref{conclusion}.

\section{Governing  Equations\label{sec:governing_eqs}}
\subsection{\label{mobility}Mobility Problem}
We consider a suspension of $N_b$ particles suspended in a
two-dimensional unbounded domain. The boundary of each particle is
denoted by $\Gamma_i$ so that $\bd \Omega = \Gamma_1 \cup \Gamma_2 \cup
\cdots \cup \Gamma_{N_b}$. Assuming the flow is Stokesian, the governing
equations are
\begin{alignat}{3}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
    && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
%
where $\uu$ is the velocity, $\mu$ is viscosity, $p$ is the pressure,
and $\uu_\infty$ is the background flow. Since each particle $\Gamma_i$
with center $\aa_i$ is a rigid body, its velocity satisfies 
\begin{align}
  \vv(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
    \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is its translational velocity and $\omega_i$ is its
angular velocity. Here, $\langle x, y \rangle^{\perp} = \langle -y, x
\rangle$. Therefore, the no-slip boundary condition on each particle is
\begin{align}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
    \xx \in \Gamma_i.
\end{align}
To determine the translational and angular velocities of each particle,
we assume some imposed forces $\FF_i$ and torques $T_i$ acting on each
particle. Since the small particles are intertialess, force balance
gives 
\begin{alignat}{2}
  \label{eqn:force}
  \FF_i &+ \int_{\Gamma_i} \ssigma \cdot \nnu_i \, ds = \mathbf{0},
  && i=1,\ldots,N_b,\\
  \label{eqn:torque}
  T_i &+ \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
    (\ssigma \cdot \nnu_i) \, ds = 0, \qquad && i=1,\ldots,N_b,
\end{alignat}
where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
\right)$ is the hydrodynamic stress tensor (pressure tensor). The
process of finding the translational and angular velocities given a
force and torque is referred to as the mobility problem.

@@

In order to examine the dynamics of the Janus-vesicle using the HAP coupling with hydrodynamics interactions, for the target bilayer, a circular initial shape is chosen to perform the relaxation run. 
This vesicle-like structure consists of $N=58$ disks with particle radius $r=0.5$ and the starting diameter of 
the vesicle is about $8.5$ length units.
The starting center of mass position of the Janus-vesicle is pinned at the origin and particle velocities are tracked to determine the initial configuration for later use such as single and multiple vesicle simulations. 
This will prevent some numerical instability issues when the minimum of the total energy is not achieved. 
For instance, the dynamics of the bilayer under a shear flow may reach different outcomes.
Figure~\ref{figure2}(a) shows that the magnitudes of mean velocity components ${\bf v}=\{v_x,v_y\}$ decrease exponentially with an approximation decaying rate $\sim0.005$. In the same figure, the variation of the mean particle orientation $\theta$ also decreases over a period of time as expected from the self-assembly property of the model. This implies that a local energy minimum and the equilibrium configuration are 
nearly attained. 
The time step size $\Delta t=0.2$ is used for all simulations in this work including the relaxation run.
Figure~\ref{figure2}(b) shows the configuration difference between starting and ending frames in the relaxation run. The Figure~\ref{figure2}(c)-(d) demonstrate the fluid pressure profile of two configurations. The pressure inside the permeable Janus-vesicle decreases as expected.

@@

Following the relaxation experiments of the Janus-vesicle, this section will focus on the behavior of vesicles 
under a number of flow types. To extract physical quantities of the target structure using the proposed model, the scaling laws and the dimensionless units are given as follows.
The length unit is scaled by the length of phospholipids $l=2.5$ nm and the force is scaled from the 
interfacial tension $\gamma=4.1$ pN nm$^{-1}$ from ~\cite{Ryham16}. We then be able to calculate the corresponding 
time scale $\tau = 0.38$ ns. With the same framework, \cite{Fu20} provides the bending rigidity 
$\kappa=8.51$ kT.

For the $N$-body Janus-vesicle, we denote a constant initial radius $R_0=\sqrt{A_0/4\pi}$ with initial area $A_0$ and the dimensionless shear rate $\chi$ is referred from~\cite{Finken08} and~\cite{Shaqfeh11},
\begin{align}
  \chi = \dot\gamma \frac{\mu R_0^2}{\kappa},
\end{align}
%
where $\dot\gamma$ the dimensional shear rate, and $\mu$ the fluid viscosity.

@@

\begin{table}
\caption{Friction Coefficients}
\centering    
\begin{tabular}{c c c c c c c c }
\hline                    
$\dot\gamma$ & 0.0020 & 0.0025 & 0.0030 & 0.0035 & 0.0040 & 0.0045 & 0.0050\\
\hline 
$F_{f}$ &  &  &  &  &  &  &   \\[1ex]
$\dot\theta$             &  &  &  &  &  &  & \\ [1ex]
$b$             &  &  &  &  &  &  & \\ 
\hline    
\end{tabular} 
\label{table1}
\end{table}

@@

\begin{figure}
\centering
\includegraphics[height=2in]{N116_ext_0.pdf}
\includegraphics[height=2in]{N116_ext_2000.pdf}\\
\includegraphics[height=2in]{N116_ext_4000.pdf}
\includegraphics[height=2in]{N116_ext_6500.pdf}
  \caption{Two vesicles under an extensional flow where the dimensioneless shear rate is $\dot\gamma=0.005$; The initial configuration is shown in panel (a). The background color indicates the magnitude of fluid pressure. From dark red to dark blue, it represents the the pressure varies from high to low values. The color bar is valid for all panels. Streamlines are plotted in purple. The insets show the results produced from using continuum model that the streamlines have perfect agreements with the present results.
  }
    \label{figure8}
\end{figure}
